---
title: "Client Reporting: the Biggest Mistakes to Avoid"
subtitle: ""  
author: 
  - "Dr Thiyanga S. Talagala"
  - ""
date: ''
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#081d58",
  text_bold_color = "#ce1256",
  title_slide_text_color = "#edf8b1",
  header_font_google = google_font("Josefin Sans"),
  base_font_size = "20px",
  text_font_size = "1.5rem"
 #text_font_google   = google_font("Montserrat", "300", "300i")
 # code_font_google   = google_font("Fira Mono")
)
```


## Client Reporting: the Biggest Mistakes

1. Making reports too long and monotonous

2. Not choosing right visuals

3. No summary of work

4. Reporting too frequently or infrequently

5. Spending too much time on report 

6. Fully automated without thinking of the client’s needs

---



## How to Create a Consulting Report?

1. Make a title page

2. Include a table of contents

3. Include an executive summary: This is to ensure that your readers have a rough idea of the report’s content and encourage them to read on

4. Write an introduction

5. Methodology/ Data Analysis

6. Summary/ Conclusions

7. Appendix

---

## Tips for Writing a Client Report

1. Maximize readability

2. Write clearly

3. Be accurate

4. Write for your audience

---

## In-class:  Errors Made on Your Reports
