---
title: "Data Quality Analysis (DQA)"
subtitle: ""  
author: 
  - "Dr Thiyanga S. Talagala"
  - ""
date: ''
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#081d58",
  text_bold_color = "#ce1256",
  title_slide_text_color = "#edf8b1",
  header_font_google = google_font("Josefin Sans"),
  base_font_size = "20px",
  text_font_size = "1.5rem"
 #text_font_google   = google_font("Montserrat", "300", "300i")
 # code_font_google   = google_font("Fira Mono")
)
```

## What is Data Quality Analysis?

Process of analyzing the quality of data in datasets to determine potential issues, shortcomings, and errors.

Missing values

- Inconsistent values

- Wrong information due to manual/ automated data errors 

- Wrong metadata information

---

## Dimensions of Data Quality Analysis

1. Consistency

2. Accuracy

3. Validity

4. Timeliness

5. Uniqueness

6. Completeness

---

Tasks in DQA

1. Data profiling

2. Data cleansing

3. Data reduction

4. Data transformation/ Data discretization

5. Data enrichment

6. Data validation
