---
title: "Meeting with Clients: Asking Good Questions, Expectations, Delivery and Conflict"
subtitle: ""  
author: 
  - "Dr Thiyanga S. Talagala"
  - ""
date: ''
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#081d58",
  text_bold_color = "#ce1256",
  title_slide_text_color = "#edf8b1",
  header_font_google = google_font("Josefin Sans"),
  base_font_size = "20px",
  text_font_size = "1.5rem"
 #text_font_google   = google_font("Montserrat", "300", "300i")
 # code_font_google   = google_font("Fira Mono")
)
```



# How does the client form their first impression of you, as a consultant?

Common courtesy and respect
obviously go a long way towards creating a positive environment for our
consultation meetings.

Non-verbal communication and verbal communication matter a lot!

Simple things you can do to help clients
feel comfortable:

- Greet the client

- Introduce yourself

---
## Asking questions

- Listen carefully to what the client says

- Listen for what is not said

- Listen $\rightarrow$ think $\rightarrow$ ask questions $\rightarrow$ learn

- Take notes **during** the consultation session

---

## Details about the client's project

- Understand the context of a project from the client's perspective

    - Background of the project
    
    - Status of the project
    
    - Aims of the project
    
    - What does the client expect from us?

- How well does the client understand the project?

- How much statistical knowledge/ technical knowledge does the client possess?

---

## What makes a question good and what makes a good question great?

A good question
elicits the information necessary to provide a correct answer to the right scientific
question.

In the context of teaching statistics, a
good question leads students to improve their understanding of statistics AND results in
the instructor better understanding how well the students have learned the context.



---

## Some questions

- Your research sounds interesting. Can you tell me more....?

- Am I understanding correctly?  **Paraphrasing the answer**

- What type of investigation is this (designed experiment, sample survey, or
observational study)?

- At what stage is this investigation (planning or analysis
stage)?

- Do certain constraints exist in the process?

- What motivated you to start this project?

- Is this a pre-specified
hypothesis you want to test, or would you
rather explore what the data have to say about the relationships?

- Who will be using these results and
how? What impacts do you hope they have

- What is the data type of each variable?

- Are there outliers or missing values present?



---

## Issues

 - The sample size is too small for any meaningful analysis or is simply
too large for our current computing resources.

- The data is biased or poorly gathered and there is no opportunity for further planned data collection.

- The client may not really understand their project or their expectations of the analysis results are unrealistic.

- We may not understand the client's project or have limited expertise
in the type of statistical analysis required for the project.

---

## Issues (cont.)

- We have moral or ethical objections to the project. This includes
statistical ethics such as a client who "requests" a particular method
of analysis which is clearly inappropriate.

Source: Cabrera, J., & McDougall, A. (2002). Statistical consulting. Springer Science & Business Media.


