---
title: "Creating Dashboards"
subtitle: ""  
author: 
  - "Dr Thiyanga S. Talagala"
  - ""
date: ''
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#081d58",
  text_bold_color = "#ce1256",
  title_slide_text_color = "#edf8b1",
  header_font_google = google_font("Josefin Sans"),
  base_font_size = "20px",
  text_font_size = "1.5rem"
 #text_font_google   = google_font("Montserrat", "300", "300i")
 # code_font_google   = google_font("Fira Mono")
)
```

class: center, inverse, middle

# What were the challenges that you faced when planning the dashboard?

---

class: center, inverse, middle

# Essential tips and considerations

---

## 1. Your audience and use cases

- Who is going to use your dashboard?

- For what purposes will they use your dashboard?

- Do not use user specific-tabs

---

## 2. Decide on the goals

What information will the user/ users be looking at?

---

## 3. Display information clearly and effectively

## 4. Communicate information quickly

Your dashboard should be,

  - simple,
  
  - easy to understand,
  
  - easy to read,
  
  - helpful without increasing **cognitive load**.
  

  

---

## 5. Select an appropriate color theme

## 6. Clear and consistent naming conventions

## 7. Effectively use the space

---

## 8. Use the right type of visualization

**What do you want to show?**

- Composition

- Comparison

- Distributions

- Relationships

**Types of visualizations**

- Static

- Dynamic

- Interactive

---

## Static

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(gganimate)
theme_set(theme_bw())
library(gapminder)
p <- ggplot(
  gapminder, 
  aes(x = gdpPercap, y=lifeExp, size = pop, colour = country)
  ) +
  geom_point(show.legend = FALSE, alpha = 0.7) +
  scale_color_viridis_d() +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  labs(x = "GDP per capita", y = "Life expectancy")
p 
```
  
---

## Interactive

```{r, echo=FALSE}
library(plotly)
ggplotly(p)
```

---
## Dynamic

```{r, echo=FALSE}
p + transition_time(year) +
  labs(title = "Year: {frame_time}")

```


---
## 9. Use interactive filters

- Chart zoom

- Drill-through

- Drill-downs

- Click-to-filters

- Cross tabs

---
## 10. Optimize for multiple screens

- Desktop

- Mobile, etc.

---

class: center, inverse

# Let's create a dashboard

Packages

library(shiny)

library(shinydashboard)

library(scemantic.dashboard)

library(flexdashboard)
